%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[letterpaper]{DS_class_file} % a4paper for A4

% Command for printing skill overview bubbles


%----------------------------------------------------------------------------------------
%	LATERAL BAR
%----------------------------------------------------------------------------------------

% Personal information
\cvname{Esteve Gallego Jutgl\`{a}} % My name.
\cvjobtitle{\hspace{0.05cm}Data Scientist} % My position.
\cvnumberphone{+32 488.674.375} % Phone number
\cvhome{Antwerpen, Belgium} % Where I live.
\cvmail{esteve.gallego.jutgla@gmail.com} % Email address
\cvlinkedin{esteve-gallego-jutgla}
\cvgithub{egallego}

% Tools information
\tools{    {\faCogs \hspace{1mm} \textbf{Other Tooling}: Spark, Kafka, git, / AWS},
{\faAreaChart \hspace{1mm} \textbf{Data Visualization}: Matplotlib, /seaborn, D3.js},
{\faLegal  \hspace{2mm} \textbf{Data Manipulation}: SciPy, NumPy/ pandas, Matlab},
{\faFlask \hspace{2mm} \textbf{Model Generation}: Sklearn, / XGBoost, TensorFlow, Keras},
{\faDatabase \hspace{2mm} \textbf{Data Storage}: PostgreSQL, MySql,/ Elastic-Search},
}

% Languages bars
\languages{{$\textbullet$ Dutch (A1) / 1 },{$\textbullet$ French (B1) / 3 },{$\textbullet$ English (C1) / 5 }, {$\textbullet$ Catalan \& Spanish (Native) / 6 }}

% Education
\education{
    \vspace{1mm}
	\textbf{PhD, Signal Processing and Machine Learning} \\
	Cum Laude \& International doctor \\
	Universitat de Vic \\
	2011 - 2015 | Vic, Barcelona, Spain

    \vspace{1mm}	
	\textbf{MSc., Information Technology} \\
	Summa Cum Laude\\
	Universitat de Vic \\
	2010 - 2011 | Vic, Barcelona, Spain

    \vspace{1mm}
	\textbf{Tech. Eng. of Telecommunications} \\
	Summa Cum Laude\\
	Universitat de Vic \\
	2005 - 2010 | Vic, Barcelona, Spain	
}




%----------------------------------------------------------------------------------------

\begin{document}

    \makeprofile % Printing sidebar

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------


    \section{Experience}

    \begin{twenty}
        \twentyitem
        {Feb 18.}
        {Present}
        {Data Scientist}
        {\href{https://www.sentiance.com/}{Sentiance}}
        {}
        {\begin{itemize}
             \item Developed an algorithm for smartphone orientation\\detection, leading to improved car events computation.
             \item Implemented a model for abnormal walking detection\\used for after-surgery recovery tracking.
             \item Improved phone handling recognition while driving,\\achieving better distracted driver profiling.
        \end{itemize}
        \textbf{Tools}: Python, TensorFlow Keras, AWS, Spark, git}
        \\
        \twentyitem
        {Sept. 2015}
        {July 2017}
        {Data Scientist}
        {\href{http://www.vilarriba.com/}{Vilar Riba}}
        {}
        {\begin{itemize}
             \item Created scoring models for targeted marketing  \\ campaigns, used to focus sales efforts.
             \item Developed of a system for product recommendation, \\ increasing number of elements bought per client.
             \item Implemented an API rest service used as endpoint \\ for recommender calls.
        \end{itemize}
        \textbf{Tools}: Python, Xgboost, Sklearn, Flask }
        \\
        \twentyitem
        {Feb. 2011}
        {Sept. 2017}
        {Assistant Professor}
        {\href{https://www.uvic.cat/}{Universitat de Vic}}
        {Subjects taught: Digital Signal Processing, Electronics \\ and Integrated Projects.}
        {}
    \end{twenty}


%----------------------------------------------------------------------------------------
%	 RESEARCH
%----------------------------------------------------------------------------------------
    \vspace{-1mm}


    \section{Research}

    \begin{twenty} % Environment for a list with descriptions
        \twentyitem
        {Research}
        {}
        {Journal Papers / Book Chapters}
        {}
        {Four articles and a book chapter published in different \\ first quartile academic journals.}
        {}
        \twentyitem
        {}
        {}
        {Proceedings of peer-reviewed international conferences}
        {}
        {Seven articles published in international conference proceedings.}
        {}
        \twentyitem
        {}
        {}
        {Research Internships}
        {}
        {Worked in different research laboratories in Japan, France,\\Singapore and Germany, for a total period of 8 months.}
        {}
    \end{twenty}


%----------------------------------------------------------------------------------------
%MENTORING
%----------------------------------------------------------------------------------------
\vspace{-1mm}


\section{Research}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem
	{Mentoring}
	{2013 - 2015}
	{FIRST Tech Challenge Mentor}
	{\href{https://twitter.com/garrinsmetalics?lang=ca}{Garrins Met\`{a}l\cdot lics}}
	{Mentored a team of 12 engineering students. Their aim was to \\participate in the FTC robot championship. Compited in different \\countries such as Spain, France, The Netherlands and USA.}
	{}
	\\
\end{twenty}


\end{document} 
